---
title: "Report"
author: "Anthony Lusardi"
date: "11/29/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}


```

|Feature name |Description|
|-----|--------|
|`date` | YMD of recorded data
|`day_week`| Day of the week
|`special_event`| Recorded if there were special events such as athletic events or school graduations
|`6_week_lun`| the 6 week trend of average guest counts for that week day at lunch
|`6_week_din`| the 6 week trend of average guest counts for that week day at dinner
|`lun_ly`| last years guests for lunch shifted for the day of the week (date-1,incomplete) 
|`din_ly`|last years guests for dinner shifted for the day of the week (date-1, incomplete)
|`din_2y`|two years ago guests for dinner shifted for the day of the week (date-2, incomplete)
|`pred_lunch`| The managers educated guess as to the amount of guest counts expected for that day at lunch
|`pred_din`|The managers educated guess as to the amount of guest counts expected for that day at dinner
|`lunch_sales`| Total sales at lunch that day (incomplete)
|`dinner_sales`| Total sales of dinner that day (incomplete)
|`guest_count_lunch`| Total guests for lunch for the given day
|`guest_count_dinner`| Total guests for dinner for the given day
|`ppl_res_lun`| Total people that are in reservations for lunch on the given day
|`ppl_res_din`| Total people that are in reservations for dinner on the given day
|`temp_avg`| The average Temperature for the day 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
